Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance

### 2022-09-12 text/Manuscript.Rmd
Upload Manuscript Figure
new behavior analysis

![**Figure 3. cPRC-specific expression of NIT-GC1 localises in close proximity to NOS in the ANS region.** (A) Expression analysis of the NIT-GC1 gene (magenta) using in situ HCR. White arrowheads indicate cells expressing NIT-GC1.Co-staining image using acetylated α-tubulin antibody (ac α-tub: green). (B) Co-expression analysis image of the c-opsin1 gene (green). Black arrowheads indicate cells expressing c-opsin1 differently from cPRC. (C and D) Localisation analysis using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (ac α-tub). (E and F) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 and NIT-GC2 knockdown by morpholino (MO1 and 2) larvae. (G-J) The intensity changes in cGMP fluorescence over time for the four conditions are shown. Gray traces show the optical responses to individual intensities (n > 6). The individual intensities are normalized (ΔF/F0). The dark line shows the mean value and the band the standard error range of the mean. The respective solution was acted on 2 min after the start of imaging (grey bars).](../figures/Fig3.png){width="100%"}

@@

![**Figure 4. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** (A) An INNOS visualised by DAF-FM is shown (a white arrowhead). A black arrowhead indicates the position of the adult eye. The white dashed line indicates the outer frame of the larva. All subsequent images are of 2-day-old larvae. (B) Dual-colour imaging of DAF-FM (green) and RGECO1a (magenta) allows simultaneous visualisation of the INNOS and cPRCs. (C) The intensity of DAF-FM in INNOS changes over time when cPRC (top) and other cells (NC) (bottom) are stimulated with UV (405 nm). Hereafter, light purple squares indicate the timing of UV stimulation, gray traces show the optical responses to individual intensities, each intensities are normalized (ΔF/F0) and the dark lines and the bands show the mean value and the standard error range of the mean. (D) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in WT (purple) and NOS mutant (NOSΔ23) (gray) larvae. (E) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 knockdown by morpholino (NITGC1-MO1 and 2) larvae. (F) Co-expression analysis image of the cPRC marker gene (NIT-GC1: magenta) and the INNOS marker gene (RYa-pNP: green) using in situ HCR. White arrowheads indicate INNOS strongly expressing RYa-pNP. (G) INNOS (blue dashed line) identified from calcium imaging using GCaMP6s by their position in relation to the cPRC (purple dashed line). (H) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INNOS (blue) when cPRC is stimulated with UV in WT (left) and NOS mutant (NOSΔ11: right) larvae. (L) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INRGW (green) when the cPRC are stimulated with UV in WT (left) and NOS mutant (NOSΔ23: right) larvae.](../figures/Fig4.png){width="100%"}

>>>>

![**Figure 3. cPRC-specific expression of NIT-GC1 localises in close proximity to NOS in the ANS region.** (A) Expression analysis of the NIT-GC1 gene (magenta) using in situ HCR. White arrowheads indicate cells expressing NIT-GC1.Co-staining image using acetylated α-tubulin antibody (ac α-tub: green). (B) Co-expression analysis image of the c-opsin1 gene (green). Black arrowheads indicate cells expressing c-opsin1 differently from cPRC. (C and D) Localisation analysis using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (ac α-tub). (E and F) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 and NIT-GC2 knockdown by morpholino (MO1 and 2) larvae. (G-J) The intensity changes in cGMP fluorescence over time for the four conditions are shown. Gray traces show the optical responses to individual intensities (n \> 6). The individual intensities are normalized (ΔF/F0). The dark line shows the mean value and the band the standard error range of the mean. The respective solution was acted on 2 min after the start of imaging (grey bars).](../figures/Fig3.png){width="100%"}

@@

![**Figure 4. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** (A) The intensity of DAF-FM in INNOS changes over time when cPRC (top) and other cells (NC) (bottom) are stimulated with UV (405 nm). Hereafter, light purple squares indicate the timing of UV stimulation, gray traces show the optical responses to individual intensities, each intensities are normalized (ΔF/F0) and the dark lines and the bands show the mean value and the standard error range of the mean. (B) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in WT (purple) and NOS mutant (NOSΔ23) (gray) larvae. (C) Changes over time in GCaMP6s intensities in cPRC when stimulated with UV in control (non-injection) and NIT-GC1 knockdown by morpholino (NITGC1-MO1 and 2) larvae. (D) Co-expression analysis image of the cPRC marker gene (NIT-GC1: magenta) and the INNOS marker gene (RYa-pNP: green) using in situ HCR. White arrowheads indicate INNOS strongly expressing RYa-pNP. (E) INNOS (blue dashed line) identified from calcium imaging using GCaMP6s by their position in relation to the cPRC (purple dashed line). (F) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INNOS (blue) when cPRC is stimulated with UV in WT (left) and NOS mutant (NOSΔ11: right) larvae. (G) Comparison of changes over time in GCaMP6s intensities in cPRC (purple) and INRGW (green) when the cPRC are stimulated with UV in WT (left) and NOS mutant (NOSΔ23: right) larvae. (H)(I)](../figures/Fig4.png){width="100%"}
